### 2014-06-03 inst/wtc-finland/manuscript.Rmd
...

#+ setup, include=FALSE
library(knitr)
opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, tidy=FALSE, fig.width=10, fig.height=15, cache=TRUE, cache.path="~/tmp/cache/")
```{r check, cache=FALSE}
message("cache path = ", opts_chunk$get("cache.path"))
```

#' NOTE: Figures and tables may be out of sync with the manuscript!
#' ----------------------------------------------------------------

@@

######
### Survey routes (Figure 1)
######

@@

######
### Number of counted survey routes
######

@@

######
### % of intersections D > 1
######

@@

######
### Crossing rates (D > 1 removed) (Figure 2)
######

@@

######
### GPS figures
######

@@

######
### GPS movements (Figure 3)
######

@@

######
### Straight-line-distance-error (Figure 4)
######

@@

######
### Raw GPS sample intervals
######

@@

######
### Power law fits for distance - sampling interval (Figure 5)
######

@@

######
### Observed distances - estimated distances (Table 1)
######

@@

# Distances from literature:
# Wolf: 7-25 km/day
# Lynx:
# FFR:

######
### Power law fit estimates for distance - sampling interval (Table 1)
######
# Fixed effects: human population density, precipitation, snow cover, temperature

@@

######
### Crude distance estimates (Table 1)
#####

@@

######
### Habitat weights (Figure 6)
######

@@

######
### Population density estimates
######

```{r population-size-init, fig.keep="none"}
plotObservations <- function(i, params) {
  subdata <- params$data[params$data$year == min(params$data$year) + i - 1,]
  subdata$Observed <- subdata$intersections>0
  geom_point(mapping=aes(coords.x1, coords.x2, colour=Observed), data=subdata)
}

@@

######
### Total population size estimates  (Figure 7)
######

```{r population-size, fig.height=5}
populationSize <- data.frame()
for (i in 1:length(responses)) {
  response <- responses[i]
  study <- FinlandWTCStudy$new(context=context, response=response)
  x <- weightedPopulationDensity[[i]]$mean$integrate(volume=FinlandPopulationSize$new(study=study))
  x$loadValidationData()
  y <- x$sizeData
  y$response <- study$getPrettyResponse(response)
  cat("Response = ", response, ", coef to match the validation data:\n")
  print(coef(x$match()))
  if (response == "canis.lupus") y$"Transformed estimated" <- y$Estimated * .7
  else if (response == "lynx.lynx") y$"Transformed estimated" <- y$Estimated / 2 *.5
  else if (response == "rangifer.tarandus.fennicus") y$"Transformed estimated" <- y$Estimated / 2 * 1.1

>>>>

```{r global_options, include=FALSE}
opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, tidy=FALSE, fig.width=10, fig.height=15, cache=TRUE, cache.path="~/tmp/cache/")
```

NOTE: Figures and tables may be out of sync with the manuscript!
----------------------------------------------------------------

@@

Survey routes (Figure 1)
------------------------

@@

Number of counted survey routes
-------------------------------

@@

% of intersections D > 1
------------------------

@@

Crossing rates (D > 1 removed) (Figure 2)
-----------------------------------------

@@

GPS figures
-----------

@@

GPS movements (Figure 3)
------------------------

@@

Straight-line-distance-error (Figure 4)
---------------------------------------

@@

Raw GPS sample intervals
------------------------

@@

Power law fits for distance - sampling interval (Figure 5)
----------------------------------------------------------

@@

Observed distances - estimated distances (Table 1)
--------------------------------------------------

@@

Distances from literature
-------------------------
* Wolf: 7-25 km/day
* Lynx:
* FFR:

Power law fit estimates for distance - sampling interval (Table 1)
------------------------------------------------------------------

Fixed effects:
* human population density
* precipitation
* snow cover
* temperature

@@

Crude distance estimates (Table 1)
----------------------------------

@@

Habitat weights (Figure 6)
--------------------------

@@

Population density estimates
----------------------------

```{r population-size-init, fig.keep="none", eval=TRUE}
plotObservations <- function(i, params) {
  subdata <- params$data[params$data$year == min(params$data$year) + i - 1,]
  subdata$Observed <- subdata$intersections>0
  geom_point(mapping=aes(coords.x1, coords.x2, colour=Observed), data=subdata)
}

@@

Total population size estimates (Figure 7)
------------------------------------------

```{r population-size, fig.height=5, eval=TRUE}
populationSize <- data.frame()
for (i in 1:length(responses)) {
  response <- responses[i]
  study <- FinlandWTCStudy$new(context=context, response=response)
  x <- weightedPopulationDensity[[i]]$mean$integrate(volume=FinlandPopulationSize$new(study=study))
  x$loadValidationData()
  y <- x$sizeData
  y$response <- study$getPrettyResponse(response)
  cat("Response = ", response, ", coef to match the validation data:\n")
  print(coef(x$match()))
  if (response == "canis.lupus") y$"Transformed estimated" <- y$Estimated * .7
  else if (response == "lynx.lynx") y$"Transformed estimated" <- y$Estimated / 2 *.5
  else if (response == "rangifer.tarandus.fennicus") y$"Transformed estimated" <- y$Estimated / 2 * 1.1
